Tables with \textbf{xtable} and \textbf{knitr}

### 2016-02-29 src/ArticleReadyTableGenerate.Rnw
add pooled stat testing. not working yet

<<Pooled_Stat_Tests>>=
 side =  c("lh","rh")
  regions = c("itg","mtg","stg","antcing","postcing")
  conditions  = c("normal","aMCI","amdMCI","nMCI","nmdMCI")
  comparisons = t(array(1,2,1,3,1,4,1,5,2,3,2,4,4,5,dim = c(2,7)))

  cond_1_fileh <- open(file = paste0(DATA_DIR,"/",side,'_',region,"_",cond_1,"_wave1_pooled_antsy.txt"))
  cond_2_fileh <- open(file = paste0(DATA_DIR,"/",side,'_',region,"_",cond_2,"_wave1_pooled_antsy.txt"))

>>>>

<<Pooled_Stat_Tests>>=
  DATA_DIR = "./data/pooled_analysis/"
 side =  c("lh","rh")
  regions = c("itg","mtg","stg","antcing","postcing")
  conditions  = c("normal","aMCI","amdMCI","nMCI","nmdMCI")
  comparisons = t(array(1,2,1,3,1,4,1,5,2,3,2,4,4,5,dim = c(2,7)))
  pooled_stats_list = list()

  #read the pooled files 
  for (i in 1:5) {
    cond_fileh <- open(file = paste0(DATA_DIR,"/",side,'_',region,"_", conditions[i], "_wave1_pooled_antsy.txt"))
    pooled_stats_list <-read.table(cond_fileh, nrows = 2.5E6, colClasses = "numeric")
    if ( is.data.frame(pooled_stats_list) ) {
      pooled_stats_list <- pooled_stats_list[,1]
    }
    pooled_stats_list <-c(pooled_stats_list, list(pool_stats)) 
  }
  # run the stat tests for the 7 pair comparisons. We may want to limi
  for ( i in 1:7 ) {
    cond_1 = comparisons[i,1]
    cond_2 = comparisons[i,2]
     pooled_test_result[[i]] <- wilcox.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
                               alternative="t",exact = FALSE,
                               correct = FALSE)
      pooled_test_result[[i]] <- ks.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
                           alternative="t",exact = NULL)

    pooled_test_result[[i]] <- ks.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],    
                                       alternative = "t",mu = 0, paired = FALSE, 
                           var.equal = FALSE, conf.level = 0.95)
